On exponential sums arising from the classical doubling method

### 2025-03-24 reorganization.tex
Adding reference to Carter

\subsubsection{Rational Tori}
A \emph{rational torus} $\algebraicGroup{T} \subseteq \algebraicGroup{G}$ over $\mathbb{F}$ is a torus defined over $\mathbb{F}$. 
Over a finite field, $\algebraicGroup{G}(\mathbb{F})$ conjugacy classes of maximal rank rational tori \calvin{check if we need connected or something} are parameterized by  Frobenius order twisted conjugacy classes in the Weyl group. In particular if you fix a rational torus $\algebraicGroup{T}_0$ with rank $=\mathrm{rk}(\algebraicGroup{G}$ and an element $g \in \algebraicGroup{G}(\algebraicClosure{\mathbb{F}})$ such that $g^{-1}\Frobenius(g) \in N(\algebraicGroup{T}_0)$ then the torus $g\algebraicGroup{T}_0g^{-1}$ is rational, and it's $\algebraicGroup{G}(\mathbb{F})$-conjugacy class is determined  by the Frobeinus-twisted conjugacy class of the image of $g^{-1}\Frobenius(g)$ in $W(\algebraicGroup{T}_0)(\algebraicClosure{\mathbb{F}})$ [cite Roger Carter Finite Groups of Lie Type section 3.3].%since $\Frobenius(g\algebraicGroup{T}_0g^{-1}) = g\algebraicGroup{T}_0g^{-1}$
%could really demonstrate this by stating Land map is surjective + that all maximal tori are conjugate over an algebraiclly closed field
Applying this theory to our groups $\algebraicGroup{G}$

>>>>

\subsubsection{Rational Tori}
A \emph{rational torus} $\algebraicGroup{T} \subseteq \algebraicGroup{G}$ over $\mathbb{F}$ is a torus defined over $\mathbb{F}$. 
Over a finite field, $\algebraicGroup{G}(\mathbb{F})$ conjugacy classes of maximal rank rational tori \calvin{check if we need connected or something} are parameterized by  Frobenius order twisted conjugacy classes in the Weyl group. In particular if you fix a rational torus $\algebraicGroup{T}_0$ with rank $=\mathrm{rk} \algebraicGroup{G}$ and an element $g \in \algebraicGroup{G}(\algebraicClosure{\mathbb{F}})$ such that $g^{-1}\Frobenius(g) \in N(\algebraicGroup{T}_0)$ then the torus $g\algebraicGroup{T}_0g^{-1}$ is rational, and it's $\algebraicGroup{G}(\mathbb{F})$-conjugacy class is determined  by the Frobeinus-twisted conjugacy class of the image of $g^{-1}\Frobenius(g)$ in $W(\algebraicGroup{T}_0)(\algebraicClosure{\mathbb{F}})$ \cite[Section 3.3]{Carter1985}.%since $\Frobenius(g\algebraicGroup{T}_0g^{-1}) = g\algebraicGroup{T}_0g^{-1}$
%could really demonstrate this by stating Land map is surjective + that all maximal tori are conjugate over an algebraiclly closed field
Applying this theory to our groups $\algebraicGroup{G}$
